{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-06 Paper/main.tex
Bspline correction

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots. On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree. Typically, knots are placed on an equidistant grid, but deviations from this principle can prove advantageous in atypical settings. Additionally, at each $\tau_l$, the polynomials on neighboring subintervals must match derivatives up to order $m-2$ at the boundary. However, it is sensible to place multiple knots at the same value to replicate specific properties of the data structure. A B-spline is a spline belonging to a basis system developed by \cite{de_boor_practical_1978}. Let $\phi_{l,m}^{BS}(x) \quad l = 1,\dots,L-1$ be the B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.

@@

@@

	{\color{red}Explain what happens when $l+m+1 > L$ !!!(I don't get it)\\
		Additionally, modify for multiple knots at the boundaries to get better behavior at the boundaries. Needs some more explanation.(adressed)}

>>>>

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing the interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots. On each subinterval, a spline is a polynomial of chosen order $m = n+1$ where $n$ is its degree. Typically, knots are placed on an equidistant grid leading to polynomials on neighboring subintervals matching derivatives up to order $m-2$ at the boundary knot $\tau_l$. However, in some settings it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure. This allows for a reduced number of matching derivatives at the corresponding knots. For the purposes of this paper, we will focus on the case of equidistant knots without multiplicity at inner knots.\\

	B-splines were developed by \cite{de_boor_practical_1978} and are defined by a recursive procedure. Let $\phi_{l,m}^{BS}(x) \quad l \in \{1,\dots,L-1\}$ be a B-spline of order $m$ for an interval $[\tau_0, \tau_L]$ and inner knots $\{\tau_l \: \vert \: l = 1,\dots, L-1\}$, then it is defined by the Cox-de Boor recursion formula as follows.

@@

	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$ an additional $m$ times. This padding of the knot vector then allows to calculate every object that is needed for the definition of the chosen basis.\\

@@
